MINOS Handover Plots

### 2023-11-30 minos/validation/handovers.Rmd

```{r}

>>>>

## Child Ages

```{r}
base.child.ages <- base.dat %>%
  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
  filter(time > 2009) %>%
  group_by(time, hidp) %>%
  summarise(child_ages = find_mode(child_ages))

s<- strsplit(base.child.ages$child_ages, "_")

base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(s, length)), expanded_child_ages = unlist(s))
base.child.ages.expanded <- base.child.ages.expanded %>%
  group_by(time, expanded_child_ages) %>%
  summarise(age_counts = n())

ggplot(data = base.child.ages.expanded, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
  geom_line() +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Year') +
  ylab('Count')

ggplot(data = base.child.ages.expanded, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
  geom_line() +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Year') +
  ylab('Count')

base.child.ages.nkids <- base.dat %>%
  group_by(time, hidp) %>%
  summarise(nkids_counts = mean(nkids)) %>%
  group_by(time) %>%
  summarise(nkids_by_year = sum(nkids_counts))

ggplot(data = base.child.ages.nkids, mapping = aes(x = time, y = nkids_by_year)) +
  geom_line() +
  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')
